Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2021-06-02 main.tex
Started fixing up simulation section text

\section{Simulation and Results} \label{sec:sim_and_results}
To demonstrate our proposed approach, we have implemented the algorithm in Section  and simulated the measurement and navigation of an object following a linear, time-invariant, process model in two-dimensional space.

Code was written in the C programming language, using the MPI library \cite{theopenmpiprojectOpenMPI2020} to support simultaneous computations by sensors and navigator as different processes. The OpenSSL library's, \cite{theopensslprojectOpenSSL2020}, mask generation function MGF1 and hash function SHA256 were used to implement the required hash function $H$, while the Libpaillier library \cite{bethencourtLibpaillier2010} was used for the implementation of the Paillier encryption scheme. Additionally, GNU libraries GSL \cite{thegsldevelopmentteamGSLGNUScientific2019} and GMP \cite{granlundGMPGNUMultiple2020} were used for algebraic operations and the handling of multiple-precision integers, respectively. Simulation execution was performed on a 3.00GHz Intel i7-9700 CPU, and run on the Windows Subsystem for Linux (WSL), where no real-time kernel was ensured but sufficiently consistent runtimes were observed for the purposes of our simulation.

Recalling the dependence of the modified measurement noise on the true measurement in \eqref{eqn:modified_measurement}, the noise distribution of the model changes with varying sizes of measurements. We considered four layouts with varying sensor distances when running our simulations to observe differences in estimation error when measurements are of different sizes. The considered layouts have been plotted and named in Figure~\ref{fig:sim_layouts}.
\begin{figure}[htbp]
\centering
\includegraphics{images/layouts.pdf}
\caption{The considered layouts, with varying average distances between navigator and sensors.}
\label{fig:sim_layouts}
\end{figure}
To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensor layouts with sensor measurement variances set to $r_i=5$ simulation units. Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $\phi$, thus, $\phi=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF. The plotted average RMSE of our proposed method as well as that of the unencrypted EIF filter can be seen in Figure \ref{fig:sim_layout_errors}.
\begin{figure}[htbp]
\centering
\includegraphics{images/layout_errors.pdf}
\caption{Filter error for different layouts, where solid lines show the results from our privacy-preserving filter and dashed lines from an unmodified EIF.}
\label{fig:sim_layout_errors}
\end{figure}
From the results, it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification from Section \ref{subsec:range_measurement_mod} has a negligible effect when compared to a normal EIF filter. The robustness of the privacy-preserving method can be attributed to the conservativeness of variance estimates in \eqref{eqn:modified_measurement_variance_estimate} and the sufficiently large fractional precision parameter $\phi$.

>>>>

\section{Simulation and Results} \label{sec:sim_and_results}
As well as having shown the theoretical backing for the security of our scheme, we have simulated the proposed localisation method to evaluate its performance. A two-dimensional linear constant velocity process model, with
\begin{equation*}
    \vec{f}_k(\vec{x}) =
    \begin{bmatrix}
        1 & 0.5 & 0 & 0\\
        0 & 1 & 0 & 0\\
        0 & 0 & 1 & 0.5\\
        0 & 0 & 0 & 1
    \end{bmatrix} \cdot \vec{x}
\end{equation*}
and
\begin{equation*}
    \mat{Q}_k = \frac{1}{10^3} \cdot
    \begin{bmatrix}
        0.4 & 1.3 & 0 & 0\\
        1.3 & 5.0 & 0 & 0\\
        0 & 0 & 0.4 & 1.3\\
        0 & 0 & 1.3 & 5.0
    \end{bmatrix}\,,
\end{equation*}
for all $k>0$, was simulated and tracked with the algorithms in section \ref{subsec:pseudocode}. Code was written in the C programming language, using the MPI library \cite{theopenmpiprojectOpenMPI2020} to support asynchronous computations by the sensors and navigator. The MG1 mask generation function and the SHA256 hash function, from the OpenSSL library \cite{theopensslprojectOpenSSL2020}, were used to implement the required hash function $H$, and the Libpaillier library \cite{bethencourtLibpaillier2010} was used for the Paillier encryption scheme. Additionally, GNU libraries, GSL \cite{thegsldevelopmentteamGSLGNUScientific2019} and GMP \cite{granlundGMPGNUMultiple2020}, were used for algebraic operations and multiple-precision encoded integers, respectively. All execution was performed on a 3.00GHz Intel i7-9700 CPU, running on the Windows Subsystem for Linux (WSL).

We have considered multiple sensor layouts, each with four sensors, to capture the dependence of estimated modified measurement variances $r_{k,i}$ on the original measurements $z_{k,i}$. The layouts, of varying sensor distances to the navigator track, are shown in figure \ref{fig:sim_layouts}.
\begin{figure}[htbp]
    \centering
    \includegraphics{images/layouts.pdf}
    \caption{The considered layouts, with varying average distances between navigator and sensors.}
    \label{fig:sim_layouts}
\end{figure}

standard EIF, equivalent to the EKF, as the baseline we comapre to

To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensor layouts with sensor measurement variances set to $r_i=5$ simulation units. Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $\phi$, thus, $\phi=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF. The plotted average RMSE of our proposed method as well as that of the unencrypted EIF filter can be seen in Figure \ref{fig:sim_layout_errors}.
\begin{figure}[htbp]
\centering
\includegraphics{images/layout_errors.pdf}
\caption{Filter error for different layouts, where solid lines show the results from our privacy-preserving filter and dashed lines from an unmodified EIF.}
\label{fig:sim_layout_errors}
\end{figure}
From the results, it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification from Section \ref{subsec:range_measurement_mod} has a negligible effect when compared to a normal EIF filter. The robustness of the privacy-preserving method can be attributed to the conservativeness of variance estimates in \eqref{eqn:modified_measurement_variance_estimate} and the sufficiently large fractional precision parameter $\phi$.
